---
title: "Study2 RI_CLPM Analysis"
author: "[anonymised for review]"
date: " "
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Analysis on the potential health consequences of burnout in athletes
This code file analyses the data from steps 1 and 2 with a random-intercept cross-lagged panel model. 

The analysis is separated into: 
- Demographic information on participants
- Descriptive statistics
- Data screening
- Correlations
- RI-CLPMs (standard, then constrained)
- Model comparisons

# Import relevant libraries
```{r libraries, warning=FALSE}
set.seed(17)
library(tidyverse)
library(lavaan)
library(ChiBarSq.DiffTest)
```

# Load in dataset
```{r load data}
dat1 <- read.csv("s2data/BOH_data.csv")
```

# Determine demographic information
```{r demographics}
##counting number of each biological sex with 1 being female and 2 being male
dat1 %>%
  group_by(bio_sex) %>%
  summarise(n())
##counting number of each sport type with 1 being individual and 2 being team sport
dat1 %>%
  group_by(sport_type) %>%
  summarise(n())
##counting number of individuals with recent injuries with 1 being No injuries and 2 being recently injured
dat1 %>%
  group_by(injury) %>%
  summarise(n())
##counting number of individuals at different times in their season: 1 being pre-season, 2 beginning of season, 3 mid-season, 4 end of season, 5 post-season
#wave1
dat1 %>%
  group_by(t1season) %>%
  summarise(n())
#wave2
dat1 %>%
  group_by(t2season) %>%
  summarise(n())
#wave3
dat1 %>%
  group_by(t3season) %>%
  summarise(n())
##counting number of people taking medication
#wave1
dat1 %>%
  filter(!is.na(t1medication)) %>%
  group_by(t1medication) %>%
  summarise(n())
#wave2
dat1 %>%
  filter(!is.na(t2medication)) %>%
  group_by(t2medication) %>%
  summarise(n())
#wave3
dat1 %>%
  filter(!is.na(t3medication)) %>%
  group_by(t3medication) %>%
  summarise(n())
##numerical demographics (mean, sd, min, max) on age, competition years
demographics <- dat1 %>%
  summarise(mean(age, na.rm = T), sd(age, na.rm=T), min(age, na.rm=T), max(age, na.rm=T), #age
            mean(comp_years, na.rm = T), sd(comp_years, na.rm=T), min(comp_years, na.rm=T), max(comp_years, na.rm = T), #competition years
            mean(t1trainingload, na.rm = T), sd(t1trainingload, na.rm=T), min(t1trainingload, na.rm = T), max(t1trainingload, na.rm = T), #wave1 training load
            mean(t2trainingload, na.rm = T), sd(t2trainingload, na.rm=T), min(t2trainingload, na.rm = T), max(t2trainingload, na.rm = T), #wave2 training load
            mean(t3trainingload, na.rm = T), sd(t3trainingload, na.rm=T), min(t3trainingload, na.rm = T), max(t3trainingload, na.rm = T)) #wave 3 training load
```

# Calculate descriptive statistics
```{r descriptive statistics}
##calculating 20% trimmed mean, sd, min, max for each variable (total burnout and symptoms, depressive symptoms, sleep quality (general score [PSQIg] and general reduced score for reliability [PSQIgr]), physical symptoms, respiratory symptoms (WURSSg as general score, WURSSc as change score), life quality) for each wave
descriptives <- dat1 %>%
  summarise(mean(t1BURN, na.rm=T, trim = 0.2), sd(t1BURN, na.rm=T), min(t1BURN, na.rm = T), max(t1BURN, na.rm = T),
            mean(t1EXH, na.rm=T, trim = 0.2), sd(t1EXH, na.rm=T), min(t1EXH, na.rm = T), max(t1EXH, na.rm = T),
            mean(t1DEV, na.rm=T, trim = 0.2), sd(t1DEV, na.rm=T), min(t1DEV, na.rm = T), max(t1DEV, na.rm = T),
            mean(t1RSA, na.rm=T, trim = 0.2), sd(t1RSA, na.rm=T), min(t1RSA, na.rm = T), max(t1RSA, na.rm = T),
            mean(t1DS, na.rm=T, trim = 0.2), sd(t1DS, na.rm=T), min(t1DS, na.rm = T), max(t1DS, na.rm = T),
            mean(t1PSQIg, na.rm=T, trim = 0.2), sd(t1PSQIg, na.rm=T), min(t1PSQIg, na.rm = T), max(t1PSQIg, na.rm = T),
            mean(t1PSQIgr, na.rm=T, trim = 0.2), sd(t1PSQIgr, na.rm=T), min(t1PSQIgr, na.rm = T), max(t1PSQIgr, na.rm = T),
            mean(t1PS, na.rm=T, trim = 0.2), sd(t1PS, na.rm=T), min(t1PS, na.rm = T), max(t1PS, na.rm = T),
            mean(t1WURSSg, na.rm=T, trim = 0.2), sd(t1WURSSg, na.rm=T), min(t1WURSSg, na.rm = T), max(t1WURSSg, na.rm = T),
            mean(t1WURSSc, na.rm=T, trim = 0.2), sd(t1WURSSc, na.rm=T), min(t1WURSSc, na.rm = T), max(t1WURSSc, na.rm = T),
            mean(t1LS, na.rm=T, trim = 0.2), sd(t1LS, na.rm=T), min(t1LS, na.rm = T), max(t1LS, na.rm = T), ##wave 1 until here
            mean(t2BURN, na.rm=T, trim = 0.2), sd(t2BURN, na.rm=T), min(t2BURN, na.rm = T), max(t2BURN, na.rm = T),
            mean(t2EXH, na.rm=T, trim = 0.2), sd(t2EXH, na.rm=T), min(t2EXH, na.rm = T), max(t2EXH, na.rm = T),
            mean(t2DEV, na.rm=T, trim = 0.2), sd(t2DEV, na.rm=T), min(t2DEV, na.rm = T), max(t2DEV, na.rm = T),
            mean(t2RSA, na.rm=T, trim = 0.2), sd(t2RSA, na.rm=T), min(t2RSA, na.rm = T), max(t2RSA, na.rm = T),
            mean(t2DS, na.rm=T, trim = 0.2), sd(t2DS, na.rm=T), min(t2DS, na.rm = T), max(t2DS, na.rm = T),
            mean(t2PSQIg, na.rm=T, trim = 0.2), sd(t2PSQIg, na.rm=T), min(t2PSQIg, na.rm = T), max(t2PSQIg, na.rm = T),
            mean(t2PSQIgr, na.rm=T, trim = 0.2), sd(t2PSQIgr, na.rm=T), min(t2PSQIgr, na.rm = T), max(t2PSQIgr, na.rm = T),
            mean(t2PS, na.rm=T, trim = 0.2), sd(t2PS, na.rm=T), min(t2PS, na.rm = T), max(t2PS, na.rm = T),
            mean(t2WURSSg, na.rm=T, trim = 0.2), sd(t2WURSSg, na.rm=T), min(t2WURSSg, na.rm = T), max(t2WURSSg, na.rm = T),
            mean(t2WURSSc, na.rm=T, trim = 0.2), sd(t2WURSSc, na.rm=T), min(t2WURSSc, na.rm = T), max(t2WURSSc, na.rm = T),
            mean(t2LS, na.rm=T, trim = 0.2), sd(t2LS, na.rm=T), min(t2LS, na.rm = T), max(t2LS, na.rm = T), ##wave 2 until here
            mean(t3BURN, na.rm=T, trim = 0.2), sd(t3BURN, na.rm=T), min(t3BURN, na.rm = T), max(t3BURN, na.rm = T),
            mean(t3EXH, na.rm=T, trim = 0.2), sd(t3EXH, na.rm=T), min(t3EXH, na.rm = T), max(t3EXH, na.rm = T),
            mean(t3DEV, na.rm=T, trim = 0.2), sd(t3DEV, na.rm=T), min(t3DEV, na.rm = T), max(t3DEV, na.rm = T),
            mean(t3RSA, na.rm=T, trim = 0.2), sd(t3RSA, na.rm=T), min(t3RSA, na.rm = T), max(t3RSA, na.rm = T),
            mean(t3DS, na.rm=T, trim = 0.2), sd(t3DS, na.rm=T), min(t3DS, na.rm = T), max(t3DS, na.rm = T),
            mean(t3PSQIg, na.rm=T, trim = 0.2), sd(t3PSQIg, na.rm=T), min(t3PSQIg, na.rm = T), max(t3PSQIg, na.rm = T),
            mean(t3PSQIgr, na.rm=T, trim = 0.2), sd(t3PSQIgr, na.rm=T), min(t3PSQIgr, na.rm = T), max(t3PSQIgr, na.rm = T),
            mean(t3PS, na.rm=T, trim = 0.2), sd(t3PS, na.rm=T), min(t3PS, na.rm = T), max(t3PS, na.rm = T),
            mean(t3WURSSg, na.rm=T, trim = 0.2), sd(t3WURSSg, na.rm=T), min(t3WURSSg, na.rm = T), max(t3WURSSg, na.rm = T),
            mean(t3WURSSc, na.rm=T, trim = 0.2), sd(t3WURSSc, na.rm=T), min(t3WURSSc, na.rm = T), max(t3WURSSc, na.rm = T),
            mean(t3LS, na.rm=T, trim = 0.2), sd(t3LS, na.rm=T), min(t3LS, na.rm = T), max(t3LS, na.rm = T)) ##wave 3 until here
##calculating mads
#wave1
mad(dat1$t1BURN, na.rm = T)
mad(dat1$t1EXH, na.rm = T)
mad(dat1$t1DEV, na.rm = T)
mad(dat1$t1RSA, na.rm = T)
mad(dat1$t1DS, na.rm = T)
mad(dat1$t1PSQIg, na.rm = T)
mad(dat1$t1PSQIgr, na.rm = T)
mad(dat1$t1PS, na.rm = T)
mad(dat1$t1WURSSg, na.rm = T)
mad(dat1$t1LS, na.rm = T)
#wave2
mad(dat1$t2BURN, na.rm = T)
mad(dat1$t2EXH, na.rm = T)
mad(dat1$t2DEV, na.rm = T)
mad(dat1$t2RSA, na.rm = T)
mad(dat1$t2DS, na.rm = T)
mad(dat1$t2PSQIg, na.rm = T)
mad(dat1$t2PSQIgr, na.rm = T)
mad(dat1$t2PS, na.rm = T)
mad(dat1$t2WURSSg, na.rm = T)
mad(dat1$t2LS, na.rm = T)
#wave3
mad(dat1$t3BURN, na.rm = T)
mad(dat1$t3EXH, na.rm = T)
mad(dat1$t3DEV, na.rm = T)
mad(dat1$t3RSA, na.rm = T)
mad(dat1$t3DS, na.rm = T)
mad(dat1$t3PSQIg, na.rm = T)
mad(dat1$t3PSQIgr, na.rm = T)
mad(dat1$t3PS, na.rm = T)
mad(dat1$t3WURSSg, na.rm = T)
mad(dat1$t3LS, na.rm = T)
```

# Assess data distribution and outliers
```{r visualisations}
## check distributions of variables at each wave
##wave 1
ggplot(dat1, aes(t1BURN))+
  geom_density()
ggplot(dat1, aes(t1EXH))+
  geom_density()
ggplot(dat1, aes(t1DEV))+
  geom_density()
ggplot(dat1, aes(t1RSA))+
  geom_density()
ggplot(dat1, aes(t1DS))+
  geom_density()
ggplot(dat1, aes(t1PSQIg))+
  geom_density()
ggplot(dat1, aes(t1PSQIgr))+
  geom_density()
ggplot(dat1, aes(t1PS))+
  geom_density()
ggplot(dat1, aes(t1WURSSg))+
  geom_density()
ggplot(dat1, aes(t1LS))+
  geom_density()

#wave 2
ggplot(dat1, aes(t2BURN))+
  geom_density()
ggplot(dat1, aes(t2EXH))+
  geom_density()
ggplot(dat1, aes(t2DEV))+
  geom_density()
ggplot(dat1, aes(t2RSA))+
  geom_density()
ggplot(dat1, aes(t2DS))+
  geom_density()
ggplot(dat1, aes(t2PSQIg))+
  geom_density()
ggplot(dat1, aes(t2PSQIgr))+
  geom_density()
ggplot(dat1, aes(t2PS))+
  geom_density()
ggplot(dat1, aes(t2WURSSg))+
  geom_density()
ggplot(dat1, aes(t2LS))+
  geom_density()

##wave 3
ggplot(dat1, aes(t3BURN))+
  geom_density()
ggplot(dat1, aes(t3EXH))+
  geom_density()
ggplot(dat1, aes(t3DEV))+
  geom_density()
ggplot(dat1, aes(t3RSA))+
  geom_density()
ggplot(dat1, aes(t3DS))+
  geom_density()
ggplot(dat1, aes(t3PSQIg))+
  geom_density()
ggplot(dat1, aes(t3PSQIgr))+
  geom_density()
ggplot(dat1, aes(t3PS))+
  geom_density()
ggplot(dat1, aes(t3WURSSg))+
  geom_density()
ggplot(dat1, aes(t3LS))+
  geom_density()

##check z-values
dat2 <- dat1 %>% 
  mutate(t1BURNz = scale(t1BURN), t1EXHz = scale(t1EXH), t1DEVz = scale(t1DEV), t1RSAz = scale(t1RSA),
         t1DSz = scale(t1DS), t1PSQIgz = scale(t1PSQIg), t1PSQIgrz = scale(t1PSQIgr), t1WURSSgz = scale(t1WURSSg), t1PSz = scale(t1PS), t1LSz = scale(t1LS), 
         t2BURNz = scale(t2BURN), t2EXHz = scale(t2EXH), t2DEVz = scale(t2DEV), t2RSAz = scale(t2RSA),
         t2DSz = scale(t2DS), t2PSQIgz = scale(t2PSQIg), t2PSQIgrz = scale(t2PSQIgr), t2WURSSgz = scale(t2WURSSg), t2PSz = scale(t2PS), t2LSz = scale(t2LS),
         t3BURNz = scale(t3BURN), t3EXHz = scale(t3EXH), t3DEVz = scale(t3DEV), t3RSAz = scale(t3RSA),
         t3DSz = scale(t3DS), t3PSQIgz = scale(t3PSQIg), t3PSQIgrz = scale(t3PSQIgr), t3WURSSgz = scale(t3WURSSg), t3PSz = scale(t3PS), t3LSz = scale(t3LS))

##create checkpoint
dat3 <- dat2

##cleaning out absolute z values over 3 by replacing them with NAs
#wave1
dat2$t1BURN <- replace(dat2$t1BURN, abs(dat2$t1BURNz) > 3, NA)
dat2$t1EXH <- replace(dat2$t1EXH, abs(dat2$t1EXHz) > 3, NA)
dat2$t1DEV <- replace(dat2$t1DEV, abs(dat2$t1DEVz) > 3, NA)
dat2$t1RSA <- replace(dat2$t1RSA, abs(dat2$t1RSAz) > 3, NA)
dat2$t1DS <- replace(dat2$t1DS, abs(dat2$t1DSz) > 3, NA)
dat2$t1PSQIg <- replace(dat2$t1PSQIg, abs(dat2$t1PSQIgz) > 3, NA)
dat2$t1PSQIgr <- replace(dat2$t1PSQIgr, abs(dat2$t1PSQIgrz) > 3, NA)
dat2$t1PS <- replace(dat2$t1PS, abs(dat2$t1PSz) > 3, NA)
dat2$t1WURSSg <- replace(dat2$t1WURSSg, abs(dat2$t1WURSSgz) > 3, NA)
dat2$t1LS <- replace(dat2$t1LS, abs(dat2$t1LSz) > 3, NA)
#wave2
dat2$t2BURN <- replace(dat2$t2BURN, abs(dat2$t2BURNz) > 3, NA)
dat2$t2EXH <- replace(dat2$t2EXH, abs(dat2$t2EXHz) > 3, NA)
dat2$t2DEV <- replace(dat2$t2DEV, abs(dat2$t2DEVz) > 3, NA)
dat2$t2RSA <- replace(dat2$t2RSA, abs(dat2$t2RSAz) > 3, NA)
dat2$t2DS <- replace(dat2$t2DS, abs(dat2$t2DSz) > 3, NA)
dat2$t2PSQIg <- replace(dat2$t2PSQIg, abs(dat2$t2PSQIgz) > 3, NA)
dat2$t2PSQIgr <- replace(dat2$t2PSQIgr, abs(dat2$t2PSQIgrz) > 3, NA)
dat2$t2PS <- replace(dat2$t2PS, abs(dat2$t2PSz) > 3, NA)
dat2$t2WURSSg <- replace(dat2$t2WURSSg, abs(dat2$t2WURSSgz) > 3, NA)
dat2$t2LS <- replace(dat2$t2LS, abs(dat2$t2LSz) > 3, NA)
#wave3
dat2$t3BURN <- replace(dat2$t3BURN, abs(dat2$t3BURNz) > 3, NA)
dat2$t3EXH <- replace(dat2$t3EXH, abs(dat2$t3EXHz) > 3, NA)
dat2$t3DEV <- replace(dat2$t3DEV, abs(dat2$t3DEVz) > 3, NA)
dat2$t3RSA <- replace(dat2$t3RSA, abs(dat2$t3RSAz) > 3, NA)
dat2$t3DS <- replace(dat2$t3DS, abs(dat2$t3DSz) > 3, NA)
dat2$t3PSQIg <- replace(dat2$t3PSQIg, abs(dat2$t3PSQIgz) > 3, NA)
dat2$t3PSQIgr <- replace(dat2$t3PSQIgr, abs(dat2$t3PSQIgrz) > 3, NA)
dat2$t3PS <- replace(dat2$t3PS, abs(dat2$t3PSz) > 3, NA)
dat2$t3WURSSg <- replace(dat2$t3WURSSg, abs(dat2$t3WURSSgz) > 3, NA)
dat2$t3LS <- replace(dat2$t3LS, abs(dat2$t3LSz) > 3, NA)
``` 

# Determine correlations for full correlation table
- dat1 has all original values, dat2 has z values and is cleaned for those, dat3 has only z-values, but is not cleaned
- all analyses post this point are run with dat2
```{r correlations}
##to calculate spearman correlations switch method = "pearson" to "spearman"
##using the replace and find option under edit at the top is the easiest way to switch out the method here 

##across wave 1
cor.test(dat2$t1BURN, dat2$t1EXH, method = "pearson")
cor.test(dat2$t1BURN, dat2$t1DEV, method = "pearson")
cor.test(dat2$t1BURN, dat2$t1RSA, method = "pearson")
cor.test(dat2$t1BURN, dat2$t1DS, method = "pearson")
cor.test(dat2$t1BURN, dat2$t1PSQIgr, method = "pearson")
cor.test(dat2$t1BURN, dat2$t1PS, method = "pearson")
cor.test(dat2$t1BURN, dat2$t1WURSSg, method = "pearson")
cor.test(dat2$t1BURN, dat2$t1LS, method = "pearson")

cor.test(dat2$t1EXH, dat2$t1DEV, method = "pearson")
cor.test(dat2$t1EXH, dat2$t1RSA, method = "pearson")
cor.test(dat2$t1EXH, dat2$t1DS, method = "pearson")
cor.test(dat2$t1EXH, dat2$t1PSQIgr, method = "pearson")
cor.test(dat2$t1EXH, dat2$t1PS, method = "pearson")
cor.test(dat2$t1EXH, dat2$t1WURSSg, method = "pearson")
cor.test(dat2$t1EXH, dat2$t1LS, method = "pearson")

cor.test(dat2$t1DEV, dat2$t1RSA, method = "pearson")
cor.test(dat2$t1DEV, dat2$t1DS, method = "pearson")
cor.test(dat2$t1DEV, dat2$t1PSQIgr, method = "pearson")
cor.test(dat2$t1DEV, dat2$t1PS, method = "pearson")
cor.test(dat2$t1DEV, dat2$t1WURSSg, method = "pearson")
cor.test(dat2$t1DEV, dat2$t1LS, method = "pearson")

cor.test(dat2$t1RSA, dat2$t1DS, method = "pearson")
cor.test(dat2$t1RSA, dat2$t1PSQIgr, method = "pearson")
cor.test(dat2$t1RSA, dat2$t1PS, method = "pearson")
cor.test(dat2$t1RSA, dat2$t1WURSSg, method = "pearson")
cor.test(dat2$t1RSA, dat2$t1LS, method = "pearson")

cor.test(dat2$t1DS, dat2$t1PSQIgr, method = "pearson")
cor.test(dat2$t1DS, dat2$t1PS, method = "pearson")
cor.test(dat2$t1DS, dat2$t1WURSSg, method = "pearson")
cor.test(dat2$t1DS, dat2$t1LS, method = "pearson")

cor.test(dat2$t1PSQIgr, dat2$t1PS, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t1WURSSg, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t1LS, method = "pearson")

cor.test(dat2$t1PS, dat2$t1WURSSg, method = "pearson")
cor.test(dat2$t1PS, dat2$t1LS, method = "pearson")

cor.test(dat2$t1WURSSg, dat2$t1LS, method = "pearson")

##across wave 2
cor.test(dat2$t2BURN, dat2$t2EXH, method = "pearson")
cor.test(dat2$t2BURN, dat2$t2DEV, method = "pearson")
cor.test(dat2$t2BURN, dat2$t2RSA, method = "pearson")
cor.test(dat2$t2BURN, dat2$t2DS, method = "pearson")
cor.test(dat2$t2BURN, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t2BURN, dat2$t2PS, method = "pearson")
cor.test(dat2$t2BURN, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t2BURN, dat2$t2LS, method = "pearson")

cor.test(dat2$t2EXH, dat2$t2DEV, method = "pearson")
cor.test(dat2$t2EXH, dat2$t2RSA, method = "pearson")
cor.test(dat2$t2EXH, dat2$t2DS, method = "pearson")
cor.test(dat2$t2EXH, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t2EXH, dat2$t2PS, method = "pearson")
cor.test(dat2$t2EXH, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t2EXH, dat2$t2LS, method = "pearson")

cor.test(dat2$t2DEV, dat2$t2RSA, method = "pearson")
cor.test(dat2$t2DEV, dat2$t2DS, method = "pearson")
cor.test(dat2$t2DEV, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t2DEV, dat2$t2PS, method = "pearson")
cor.test(dat2$t2DEV, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t2DEV, dat2$t2LS, method = "pearson")

cor.test(dat2$t2RSA, dat2$t2DS, method = "pearson")
cor.test(dat2$t2RSA, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t2RSA, dat2$t2PS, method = "pearson")
cor.test(dat2$t2RSA, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t2RSA, dat2$t2LS, method = "pearson")

cor.test(dat2$t2DS, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t2DS, dat2$t2PS, method = "pearson")
cor.test(dat2$t2DS, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t2DS, dat2$t2LS, method = "pearson")

cor.test(dat2$t2PSQIgr, dat2$t2PS, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t2LS, method = "pearson")

cor.test(dat2$t2PS, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t2PS, dat2$t2LS, method = "pearson")

cor.test(dat2$t2WURSSg, dat2$t2LS, method = "pearson")

##across wave 3
cor.test(dat2$t3BURN, dat2$t3EXH, method = "pearson")
cor.test(dat2$t3BURN, dat2$t3DEV, method = "pearson")
cor.test(dat2$t3BURN, dat2$t3RSA, method = "pearson")
cor.test(dat2$t3BURN, dat2$t3DS, method = "pearson")
cor.test(dat2$t3BURN, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t3BURN, dat2$t3PS, method = "pearson")
cor.test(dat2$t3BURN, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t3BURN, dat2$t3LS, method = "pearson")

cor.test(dat2$t3EXH, dat2$t3DEV, method = "pearson")
cor.test(dat2$t3EXH, dat2$t3RSA, method = "pearson")
cor.test(dat2$t3EXH, dat2$t3DS, method = "pearson")
cor.test(dat2$t3EXH, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t3EXH, dat2$t3PS, method = "pearson")
cor.test(dat2$t3EXH, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t3EXH, dat2$t3LS, method = "pearson")

cor.test(dat2$t3DEV, dat2$t3RSA, method = "pearson")
cor.test(dat2$t3DEV, dat2$t3DS, method = "pearson")
cor.test(dat2$t3DEV, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t3DEV, dat2$t3PS, method = "pearson")
cor.test(dat2$t3DEV, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t3DEV, dat2$t3LS, method = "pearson")

cor.test(dat2$t3RSA, dat2$t3DS, method = "pearson")
cor.test(dat2$t3RSA, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t3RSA, dat2$t3PS, method = "pearson")
cor.test(dat2$t3RSA, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t3RSA, dat2$t3LS, method = "pearson")

cor.test(dat2$t3DS, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t3DS, dat2$t3PS, method = "pearson")
cor.test(dat2$t3DS, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t3DS, dat2$t3LS, method = "pearson")

cor.test(dat2$t3PSQIgr, dat2$t3PS, method = "pearson")
cor.test(dat2$t3PSQIgr, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t3PSQIgr, dat2$t3LS, method = "pearson")

cor.test(dat2$t3PS, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t3PS, dat2$t3LS, method = "pearson")

cor.test(dat2$t3WURSSg, dat2$t3LS, method = "pearson")

##wave 1 on wave 2
cor.test(dat2$t1BURN, dat2$t2BURN, method = "pearson")
cor.test(dat2$t1BURN, dat2$t2EXH, method = "pearson")
cor.test(dat2$t1BURN, dat2$t2DEV, method = "pearson")
cor.test(dat2$t1BURN, dat2$t2RSA, method = "pearson")
cor.test(dat2$t1BURN, dat2$t2DS, method = "pearson")
cor.test(dat2$t1BURN, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t1BURN, dat2$t2PS, method = "pearson")
cor.test(dat2$t1BURN, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t1BURN, dat2$t2LS, method = "pearson")

cor.test(dat2$t1EXH, dat2$t2BURN, method = "pearson")
cor.test(dat2$t1EXH, dat2$t2EXH, method = "pearson")
cor.test(dat2$t1EXH, dat2$t2DEV, method = "pearson")
cor.test(dat2$t1EXH, dat2$t2RSA, method = "pearson")
cor.test(dat2$t1EXH, dat2$t2DS, method = "pearson")
cor.test(dat2$t1EXH, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t1EXH, dat2$t2PS, method = "pearson")
cor.test(dat2$t1EXH, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t1EXH, dat2$t2LS, method = "pearson")

cor.test(dat2$t1DEV, dat2$t2BURN, method = "pearson")
cor.test(dat2$t1DEV, dat2$t2EXH, method = "pearson")
cor.test(dat2$t1DEV, dat2$t2DEV, method = "pearson")
cor.test(dat2$t1DEV, dat2$t2RSA, method = "pearson")
cor.test(dat2$t1DEV, dat2$t2DS, method = "pearson")
cor.test(dat2$t1DEV, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t1DEV, dat2$t2PS, method = "pearson")
cor.test(dat2$t1DEV, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t1DEV, dat2$t2LS, method = "pearson")

cor.test(dat2$t1RSA, dat2$t2BURN, method = "pearson")
cor.test(dat2$t1RSA, dat2$t2EXH, method = "pearson")
cor.test(dat2$t1RSA, dat2$t2DEV, method = "pearson")
cor.test(dat2$t1RSA, dat2$t2RSA, method = "pearson")
cor.test(dat2$t1RSA, dat2$t2DS, method = "pearson")
cor.test(dat2$t1RSA, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t1RSA, dat2$t2PS, method = "pearson")
cor.test(dat2$t1RSA, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t1RSA, dat2$t2LS, method = "pearson")

cor.test(dat2$t1DS, dat2$t2BURN, method = "pearson")
cor.test(dat2$t1DS, dat2$t2EXH, method = "pearson")
cor.test(dat2$t1DS, dat2$t2DEV, method = "pearson")
cor.test(dat2$t1DS, dat2$t2RSA, method = "pearson")
cor.test(dat2$t1DS, dat2$t2DS, method = "pearson")
cor.test(dat2$t1DS, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t1DS, dat2$t2PS, method = "pearson")
cor.test(dat2$t1DS, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t1DS, dat2$t2LS, method = "pearson")

cor.test(dat2$t1PSQIgr, dat2$t2BURN, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t2EXH, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t2DEV, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t2RSA, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t2DS, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t2PS, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t2LS, method = "pearson")

cor.test(dat2$t1PS, dat2$t2BURN, method = "pearson")
cor.test(dat2$t1PS, dat2$t2EXH, method = "pearson")
cor.test(dat2$t1PS, dat2$t2DEV, method = "pearson")
cor.test(dat2$t1PS, dat2$t2RSA, method = "pearson")
cor.test(dat2$t1PS, dat2$t2DS, method = "pearson")
cor.test(dat2$t1PS, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t1PS, dat2$t2PS, method = "pearson")
cor.test(dat2$t1PS, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t1PS, dat2$t2LS, method = "pearson")

cor.test(dat2$t1WURSSg, dat2$t2BURN, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t2EXH, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t2DEV, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t2RSA, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t2DS, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t2PS, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t1LS, method = "pearson")

cor.test(dat2$t1LS, dat2$t2BURN, method = "pearson")
cor.test(dat2$t1LS, dat2$t2EXH, method = "pearson")
cor.test(dat2$t1LS, dat2$t2DEV, method = "pearson")
cor.test(dat2$t1LS, dat2$t2RSA, method = "pearson")
cor.test(dat2$t1LS, dat2$t2DS, method = "pearson")
cor.test(dat2$t1LS, dat2$t2PSQIgr, method = "pearson")
cor.test(dat2$t1LS, dat2$t2PS, method = "pearson")
cor.test(dat2$t1LS, dat2$t2WURSSg, method = "pearson")
cor.test(dat2$t1LS, dat2$t2LS, method = "pearson")

##wave 1 on wave 3
cor.test(dat2$t1BURN, dat2$t3BURN, method = "pearson")
cor.test(dat2$t1BURN, dat2$t3EXH, method = "pearson")
cor.test(dat2$t1BURN, dat2$t3DEV, method = "pearson")
cor.test(dat2$t1BURN, dat2$t3RSA, method = "pearson")
cor.test(dat2$t1BURN, dat2$t3DS, method = "pearson")
cor.test(dat2$t1BURN, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t1BURN, dat2$t3PS, method = "pearson")
cor.test(dat2$t1BURN, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t1BURN, dat2$t3LS, method = "pearson")

cor.test(dat2$t1EXH, dat2$t3BURN, method = "pearson")
cor.test(dat2$t1EXH, dat2$t3EXH, method = "pearson")
cor.test(dat2$t1EXH, dat2$t3DEV, method = "pearson")
cor.test(dat2$t1EXH, dat2$t3RSA, method = "pearson")
cor.test(dat2$t1EXH, dat2$t3DS, method = "pearson")
cor.test(dat2$t1EXH, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t1EXH, dat2$t3PS, method = "pearson")
cor.test(dat2$t1EXH, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t1EXH, dat2$t3LS, method = "pearson")

cor.test(dat2$t1DEV, dat2$t3BURN, method = "pearson")
cor.test(dat2$t1DEV, dat2$t3EXH, method = "pearson")
cor.test(dat2$t1DEV, dat2$t3DEV, method = "pearson")
cor.test(dat2$t1DEV, dat2$t3RSA, method = "pearson")
cor.test(dat2$t1DEV, dat2$t3DS, method = "pearson")
cor.test(dat2$t1DEV, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t1DEV, dat2$t3PS, method = "pearson")
cor.test(dat2$t1DEV, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t1DEV, dat2$t3LS, method = "pearson")

cor.test(dat2$t1RSA, dat2$t3BURN, method = "pearson")
cor.test(dat2$t1RSA, dat2$t3EXH, method = "pearson")
cor.test(dat2$t1RSA, dat2$t3DEV, method = "pearson")
cor.test(dat2$t1RSA, dat2$t3RSA, method = "pearson")
cor.test(dat2$t1RSA, dat2$t3DS, method = "pearson")
cor.test(dat2$t1RSA, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t1RSA, dat2$t3PS, method = "pearson")
cor.test(dat2$t1RSA, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t1RSA, dat2$t3LS, method = "pearson")

cor.test(dat2$t1DS, dat2$t3BURN, method = "pearson")
cor.test(dat2$t1DS, dat2$t3EXH, method = "pearson")
cor.test(dat2$t1DS, dat2$t3DEV, method = "pearson")
cor.test(dat2$t1DS, dat2$t3RSA, method = "pearson")
cor.test(dat2$t1DS, dat2$t3DS, method = "pearson")
cor.test(dat2$t1DS, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t1DS, dat2$t3PS, method = "pearson")
cor.test(dat2$t1DS, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t1DS, dat2$t3LS, method = "pearson")

cor.test(dat2$t1PSQIgr, dat2$t3BURN, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t3EXH, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t3DEV, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t3RSA, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t3DS, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t3PS, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t1PSQIgr, dat2$t3LS, method = "pearson")

cor.test(dat2$t1PS, dat2$t3BURN, method = "pearson")
cor.test(dat2$t1PS, dat2$t3EXH, method = "pearson")
cor.test(dat2$t1PS, dat2$t3DEV, method = "pearson")
cor.test(dat2$t1PS, dat2$t3RSA, method = "pearson")
cor.test(dat2$t1PS, dat2$t3DS, method = "pearson")
cor.test(dat2$t1PS, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t1PS, dat2$t3PS, method = "pearson")
cor.test(dat2$t1PS, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t1PS, dat2$t3LS, method = "pearson")

cor.test(dat2$t1WURSSg, dat2$t3BURN, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t3EXH, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t3DEV, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t3RSA, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t3DS, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t3PS, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t1WURSSg, dat2$t3LS, method = "pearson")

cor.test(dat2$t1LS, dat2$t3BURN, method = "pearson")
cor.test(dat2$t1LS, dat2$t3EXH, method = "pearson")
cor.test(dat2$t1LS, dat2$t3DEV, method = "pearson")
cor.test(dat2$t1LS, dat2$t3RSA, method = "pearson")
cor.test(dat2$t1LS, dat2$t3DS, method = "pearson")
cor.test(dat2$t1LS, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t1LS, dat2$t3PS, method = "pearson")
cor.test(dat2$t1LS, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t1LS, dat2$t3LS, method = "pearson")

#wave 2 on wave 3
cor.test(dat2$t2BURN, dat2$t3BURN, method = "pearson")
cor.test(dat2$t2BURN, dat2$t3EXH, method = "pearson")
cor.test(dat2$t2BURN, dat2$t3DEV, method = "pearson")
cor.test(dat2$t2BURN, dat2$t3RSA, method = "pearson")
cor.test(dat2$t2BURN, dat2$t3DS, method = "pearson")
cor.test(dat2$t2BURN, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t2BURN, dat2$t3PS, method = "pearson")
cor.test(dat2$t2BURN, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t2BURN, dat2$t3LS, method = "pearson")

cor.test(dat2$t2EXH, dat2$t3BURN, method = "pearson")
cor.test(dat2$t2EXH, dat2$t3EXH, method = "pearson")
cor.test(dat2$t2EXH, dat2$t3DEV, method = "pearson")
cor.test(dat2$t2EXH, dat2$t3RSA, method = "pearson")
cor.test(dat2$t2EXH, dat2$t3DS, method = "pearson")
cor.test(dat2$t2EXH, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t2EXH, dat2$t3PS, method = "pearson")
cor.test(dat2$t2EXH, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t2EXH, dat2$t3LS, method = "pearson")

cor.test(dat2$t2DEV, dat2$t3BURN, method = "pearson")
cor.test(dat2$t2DEV, dat2$t3EXH, method = "pearson")
cor.test(dat2$t2DEV, dat2$t3DEV, method = "pearson")
cor.test(dat2$t2DEV, dat2$t3RSA, method = "pearson")
cor.test(dat2$t2DEV, dat2$t3DS, method = "pearson")
cor.test(dat2$t2DEV, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t2DEV, dat2$t3PS, method = "pearson")
cor.test(dat2$t2DEV, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t2DEV, dat2$t3LS, method = "pearson")

cor.test(dat2$t2RSA, dat2$t3BURN, method = "pearson")
cor.test(dat2$t2RSA, dat2$t3EXH, method = "pearson")
cor.test(dat2$t2RSA, dat2$t3DEV, method = "pearson")
cor.test(dat2$t2RSA, dat2$t3RSA, method = "pearson")
cor.test(dat2$t2RSA, dat2$t3DS, method = "pearson")
cor.test(dat2$t2RSA, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t2RSA, dat2$t3PS, method = "pearson")
cor.test(dat2$t2RSA, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t2RSA, dat2$t3LS, method = "pearson")

cor.test(dat2$t2DS, dat2$t3BURN, method = "pearson")
cor.test(dat2$t2DS, dat2$t3EXH, method = "pearson")
cor.test(dat2$t2DS, dat2$t3DEV, method = "pearson")
cor.test(dat2$t2DS, dat2$t3RSA, method = "pearson")
cor.test(dat2$t2DS, dat2$t3DS, method = "pearson")
cor.test(dat2$t2DS, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t2DS, dat2$t3PS, method = "pearson")
cor.test(dat2$t2DS, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t2DS, dat2$t3LS, method = "pearson")

cor.test(dat2$t2PSQIgr, dat2$t3BURN, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t3EXH, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t3DEV, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t3RSA, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t3DS, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t3PS, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t2PSQIgr, dat2$t3LS, method = "pearson")

cor.test(dat2$t2PS, dat2$t3BURN, method = "pearson")
cor.test(dat2$t2PS, dat2$t3EXH, method = "pearson")
cor.test(dat2$t2PS, dat2$t3DEV, method = "pearson")
cor.test(dat2$t2PS, dat2$t3RSA, method = "pearson")
cor.test(dat2$t2PS, dat2$t3DS, method = "pearson")
cor.test(dat2$t2PS, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t2PS, dat2$t3PS, method = "pearson")
cor.test(dat2$t2PS, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t2PS, dat2$t3LS, method = "pearson")

cor.test(dat2$t2WURSSg, dat2$t3BURN, method = "pearson")
cor.test(dat2$t2WURSSg, dat2$t3EXH, method = "pearson")
cor.test(dat2$t2WURSSg, dat2$t3DEV, method = "pearson")
cor.test(dat2$t2WURSSg, dat2$t3RSA, method = "pearson")
cor.test(dat2$t2WURSSg, dat2$t3DS, method = "pearson")
cor.test(dat2$t2WURSSg, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t2WURSSg, dat2$t3PS, method = "pearson")
cor.test(dat2$t2WURSSg, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t2WURSSg, dat2$t3LS, method = "pearson")

cor.test(dat2$t2LS, dat2$t3BURN, method = "pearson")
cor.test(dat2$t2LS, dat2$t3EXH, method = "pearson")
cor.test(dat2$t2LS, dat2$t3DEV, method = "pearson")
cor.test(dat2$t2LS, dat2$t3RSA, method = "pearson")
cor.test(dat2$t2LS, dat2$t3DS, method = "pearson")
cor.test(dat2$t2LS, dat2$t3PSQIgr, method = "pearson")
cor.test(dat2$t2LS, dat2$t3PS, method = "pearson")
cor.test(dat2$t2LS, dat2$t3WURSSg, method = "pearson")
cor.test(dat2$t2LS, dat2$t3LS, method = "pearson")
```

# Run RI-CLPMs: Standard Models
All RI-CLPM and model comparison code follows Mulder and Hamaker (2021), link to repository for example code: https://jeroendmulder.github.io/RI-CLPM/lavaan.html
Please cite their paper when referring to modelling and the provided code. 
```{r RI-CLPM}
##depressive symptoms
#burnout
RICLPM_DS_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN 
  RIy =~ 1*t1DS + 1*t2DS + 1*t3DS
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1DS
  wy2 =~ 1*t2DS
  wy3 =~ 1*t3DS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_DS_B.fit <- lavaan(RICLPM_DS_B,
  data = dat2, 
  missing = "ML",
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_DS_B.fit, fit.measures=T, standardized = T, rsquare=T)
standardizedsolution(RICLPM_DS_B.fit) ##for confidence intervals

#exhaustion
RICLPM_DS_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH 
  RIy =~ 1*t1DS + 1*t2DS + 1*t3DS
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1DS
  wy2 =~ 1*t2DS
  wy3 =~ 1*t3DS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_DS_EXH.fit <- lavaan(RICLPM_DS_EXH,
  data = dat2, 
  missing = "ML",
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_DS_EXH.fit, fit.measures=T, standardized = T, rsquare=T)
standardizedsolution(RICLPM_DS_EXH.fit)

#devaluation
RICLPM_DS_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV
  RIy =~ 1*t1DS + 1*t2DS + 1*t3DS
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1DS
  wy2 =~ 1*t2DS
  wy3 =~ 1*t3DS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_DS_DEV.fit <- lavaan(RICLPM_DS_DEV,
  data = dat2, 
  missing = "ML",
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_DS_DEV.fit, fit.measures=T, standardized = T, rsquare=T)
standardizedsolution(RICLPM_DS_DEV.fit)

#reduced sense of accomplishment
RICLPM_DS_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA 
  RIy =~ 1*t1DS + 1*t2DS + 1*t3DS
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1DS
  wy2 =~ 1*t2DS
  wy3 =~ 1*t3DS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_DS_RSA.fit <- lavaan(RICLPM_DS_RSA,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_DS_RSA.fit, fit.measures=T, standardized = T, rsquare=T)
standardizedsolution(RICLPM_DS_RSA.fit)

##sleep quality
#burnout
RICLPM_SQ_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN 
  RIy =~ 1*t1PSQIgr + 1*t2PSQIgr + 1*t3PSQIgr
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1PSQIgr
  wy2 =~ 1*t2PSQIgr
  wy3 =~ 1*t3PSQIgr

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_SQ_B.fit <- lavaan(RICLPM_SQ_B,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_SQ_B.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_SQ_B.fit)

#exhaustion
RICLPM_SQ_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH 
  RIy =~ 1*t1PSQIgr + 1*t2PSQIgr + 1*t3PSQIgr
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1PSQIgr
  wy2 =~ 1*t2PSQIgr
  wy3 =~ 1*t3PSQIgr

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_SQ_EXH.fit <- lavaan(RICLPM_SQ_EXH,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_SQ_EXH.fit, fit.measures=T, standardized = T, rsquare=T)
standardizedsolution(RICLPM_SQ_EXH.fit)

#devaluation
RICLPM_SQ_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV 
  RIy =~ 1*t1PSQIgr + 1*t2PSQIgr + 1*t3PSQIgr
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1PSQIgr
  wy2 =~ 1*t2PSQIgr
  wy3 =~ 1*t3PSQIgr

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_SQ_DEV.fit <- lavaan(RICLPM_SQ_DEV,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_SQ_DEV.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_SQ_DEV.fit)

#reduced sense of accomplishment
RICLPM_SQ_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA
  RIy =~ 1*t1PSQIgr + 1*t2PSQIgr + 1*t3PSQIgr
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1PSQIgr
  wy2 =~ 1*t2PSQIgr
  wy3 =~ 1*t3PSQIgr

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_SQ_RSA.fit <- lavaan(RICLPM_SQ_RSA,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_SQ_RSA.fit, fit.measures = T, standardized = T)
standardizedsolution(RICLPM_SQ_RSA.fit)

##physical symptoms
#burnout
RICLPM_PS_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN 
  RIy =~ 1*t1PS + 1*t2PS + 1*t3PS
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1PS
  wy2 =~ 1*t2PS
  wy3 =~ 1*t3PS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_PS_B.fit <- lavaan(RICLPM_PS_B,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_PS_B.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_PS_B.fit)

#exhaustion
RICLPM_PS_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH
  RIy =~ 1*t1PS + 1*t2PS + 1*t3PS
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1PS
  wy2 =~ 1*t2PS
  wy3 =~ 1*t3PS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_PS_EXH.fit <- lavaan(RICLPM_PS_EXH,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_PS_EXH.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_PS_EXH.fit)

#devaluation
RICLPM_PS_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV
  RIy =~ 1*t1PS + 1*t2PS + 1*t3PS
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1PS
  wy2 =~ 1*t2PS
  wy3 =~ 1*t3PS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_PS_DEV.fit <- lavaan(RICLPM_PS_DEV,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_PS_DEV.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_PS_DEV.fit)

#reduced sense of accomplishment
RICLPM_PS_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA
  RIy =~ 1*t1PS + 1*t2PS + 1*t3PS
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1PS
  wy2 =~ 1*t2PS
  wy3 =~ 1*t3PS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_PS_RSA.fit <- lavaan(RICLPM_PS_RSA,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_PS_RSA.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_PS_RSA.fit)


##respiratory symptoms
#burnout
RICLPM_URS_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN
  RIy =~ 1*t1WURSSg + 1*t2WURSSg + 1*t3WURSSg
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1WURSSg
  wy2 =~ 1*t2WURSSg
  wy3 =~ 1*t3WURSSg

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_URS_B.fit <- lavaan(RICLPM_URS_B,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_URS_B.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_URS_B.fit)

#exhaustion
RICLPM_URS_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH
  RIy =~ 1*t1WURSSg + 1*t2WURSSg + 1*t3WURSSg
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1WURSSg
  wy2 =~ 1*t2WURSSg
  wy3 =~ 1*t3WURSSg

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_URS_EXH.fit <- lavaan(RICLPM_URS_EXH,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_URS_EXH.fit, fit.measures=T, standardized = T) ##does not converge

#devaluation
RICLPM_URS_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV
  RIy =~ 1*t1WURSSg + 1*t2WURSSg + 1*t3WURSSg
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1WURSSg
  wy2 =~ 1*t2WURSSg
  wy3 =~ 1*t3WURSSg

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_URS_DEV.fit <- lavaan(RICLPM_URS_DEV,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_URS_DEV.fit, fit.measures=T, standardized = T) ##misspecified

#reduced sense of accomplishment
RICLPM_URS_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA
  RIy =~ 1*t1WURSSg + 1*t2WURSSg + 1*t3WURSSg
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1WURSSg
  wy2 =~ 1*t2WURSSg
  wy3 =~ 1*t3WURSSg

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_URS_RSA.fit <- lavaan(RICLPM_URS_RSA,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_URS_RSA.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_URS_RSA.fit)

##life satisfaction
#burnout
RICLPM_LS_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN
  RIy =~ 1*t1LS + 1*t2LS + 1*t3LS
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1LS
  wy2 =~ 1*t2LS
  wy3 =~ 1*t3LS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_LS_B.fit <- lavaan(RICLPM_LS_B,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_LS_B.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_LS_B.fit)

#exhaustion
RICLPM_LS_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH
  RIy =~ 1*t1LS + 1*t2LS + 1*t3LS
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1LS
  wy2 =~ 1*t2LS
  wy3 =~ 1*t3LS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_LS_EXH.fit <- lavaan(RICLPM_LS_EXH,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_LS_EXH.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_LS_EXH.fit)

#devaluation
RICLPM_LS_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV
  RIy =~ 1*t1LS + 1*t2LS + 1*t3LS
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1LS
  wy2 =~ 1*t2LS
  wy3 =~ 1*t3LS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_LS_DEV.fit <- lavaan(RICLPM_LS_DEV,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_LS_DEV.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_LS_DEV.fit)

#reduced sense of accomplishment
RICLPM_LS_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA
  RIy =~ 1*t1LS + 1*t2LS + 1*t3LS
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1LS
  wy2 =~ 1*t2LS
  wy3 =~ 1*t3LS

  # Estimate lagged effects between within-person centered variables
  wx2 + wy2 ~ wx1 + wy1
  wx3 + wy3 ~ wx2 + wy2

  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPM_LS_RSA.fit <- lavaan(RICLPM_LS_RSA,
  data = dat2, 
  missing = "ML", 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
)

summary(RICLPM_LS_RSA.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPM_LS_RSA.fit)
```

# RI-CLPMs with constraints
Constraints are placed on lagged effects
```{r RI-CLPM restrictions}
##depressive symptoms
#burnout
RICLPMr_DS_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN
  RIy =~ 1*t1DS + 1*t2DS + 1*t3DS
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1DS
  wy2 =~ 1*t2DS
  wy3 =~ 1*t3DS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 
  
'
RICLPMr_DS_B.fit <- lavaan(RICLPMr_DS_B, 
  data = dat2, 
  missing = 'ML', 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_DS_B.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_DS_B.fit)

#exhaustion
RICLPMr_DS_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH
  RIy =~ 1*t1DS + 1*t2DS + 1*t3DS
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1DS
  wy2 =~ 1*t2DS
  wy3 =~ 1*t3DS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 
  
'
RICLPMr_DS_EXH.fit <- lavaan(RICLPMr_DS_EXH, 
  data = dat2, 
  missing = 'ML',#
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_DS_EXH.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_DS_EXH.fit)

#devaluation
RICLPMr_DS_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV
  RIy =~ 1*t1DS + 1*t2DS + 1*t3DS
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1DS
  wy2 =~ 1*t2DS
  wy3 =~ 1*t3DS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_DS_DEV.fit <- lavaan(RICLPMr_DS_DEV, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_DS_DEV.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_DS_DEV.fit)

#RSA
RICLPMr_DS_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA
  RIy =~ 1*t1DS + 1*t2DS + 1*t3DS
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1DS
  wy2 =~ 1*t2DS
  wy3 =~ 1*t3DS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_DS_RSA.fit <- lavaan(RICLPMr_DS_RSA, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_DS_RSA.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_DS_RSA.fit)

##sleep quality
#burnout
RICLPMr_SQ_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN
  RIy =~ 1*t1PSQIgr + 1*t2PSQIgr + 1*t3PSQIgr
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1PSQIgr
  wy2 =~ 1*t2PSQIgr
  wy3 =~ 1*t3PSQIgr
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_SQ_B.fit <- lavaan(RICLPMr_SQ_B, 
  data = dat2, 
  missing = 'ML', 
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_SQ_B.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_SQ_B.fit)

#exhaustion
RICLPMr_SQ_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH
  RIy =~ 1*t1PSQIgr + 1*t2PSQIgr + 1*t3PSQIgr
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1PSQIgr
  wy2 =~ 1*t2PSQIgr
  wy3 =~ 1*t3PSQIgr
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_SQ_EXH.fit <- lavaan(RICLPMr_SQ_EXH, 
  data = dat2, 
  missing = 'ML', 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_SQ_EXH.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_SQ_EXH.fit)

#devaluation
RICLPMr_SQ_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV
  RIy =~ 1*t1PSQIgr + 1*t2PSQIgr + 1*t3PSQIgr
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1PSQIgr
  wy2 =~ 1*t2PSQIgr
  wy3 =~ 1*t3PSQIgr
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_SQ_DEV.fit <- lavaan(RICLPMr_SQ_DEV, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_SQ_DEV.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_SQ_DEV.fit)

#RSA
RICLPMr_SQ_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA
  RIy =~ 1*t1PSQIg + 1*t2PSQIg + 1*t3PSQIg
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1PSQIg
  wy2 =~ 1*t2PSQIg
  wy3 =~ 1*t3PSQIg
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_SQ_RSA.fit <- lavaan(RICLPMr_SQ_RSA, 
  data = dat2, 
  missing = 'ML', 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_SQ_RSA.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_SQ_RSA.fit)

##physical symptoms
RICLPMr_PS_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN
  RIy =~ 1*t1PS + 1*t2PS + 1*t3PS
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1PS
  wy2 =~ 1*t2PS
  wy3 =~ 1*t3PS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_PS_B.fit <- lavaan(RICLPMr_PS_B, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_PS_B.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_PS_B.fit)

#exhaustion
RICLPMr_PS_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH
  RIy =~ 1*t1PS + 1*t2PS + 1*t3PS
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1PS
  wy2 =~ 1*t2PS
  wy3 =~ 1*t3PS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_PS_EXH.fit <- lavaan(RICLPMr_PS_EXH, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_PS_EXH.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_PS_EXH.fit)

#devaluation
RICLPMr_PS_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV
  RIy =~ 1*t1PS + 1*t2PS + 1*t3PS
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1PS
  wy2 =~ 1*t2PS
  wy3 =~ 1*t3PS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_PS_DEV.fit <- lavaan(RICLPMr_PS_DEV, 
  data = dat2, 
  missing = 'ML', 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_PS_DEV.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_PS_DEV.fit)

#RSA
RICLPMr_PS_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA
  RIy =~ 1*t1PS + 1*t2PS + 1*t3PS
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1PS
  wy2 =~ 1*t2PS
  wy3 =~ 1*t3PS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_PS_RSA.fit <- lavaan(RICLPMr_PS_RSA, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_PS_RSA.fit, fit.measures = T, standardized = T)
standardizedsolution(RICLPMr_PS_RSA.fit)

##respiratory symptoms
RICLPMr_URS_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN
  RIy =~ 1*t1WURSSg + 1*t2WURSSg + 1*t3WURSSg
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1WURSSg
  wy2 =~ 1*t2WURSSg
  wy3 =~ 1*t3WURSSg
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_URS_B.fit <- lavaan(RICLPMr_URS_B, 
  data = dat2, 
  missing = 'ML', 
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_URS_B.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_URS_B.fit)

#exhaustion
RICLPMr_URS_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH
  RIy =~ 1*t1WURSSg + 1*t2WURSSg + 1*t3WURSSg
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1WURSSg
  wy2 =~ 1*t2WURSSg
  wy3 =~ 1*t3WURSSg
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_URS_EXH.fit <- lavaan(RICLPMr_URS_EXH, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_URS_EXH.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_URS_EXH.fit)

#devaluation
RICLPMr_URS_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV
  RIy =~ 1*t1WURSSg + 1*t2WURSSg + 1*t3WURSSg
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1WURSSg
  wy2 =~ 1*t2WURSSg
  wy3 =~ 1*t3WURSSg
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_URS_DEV.fit <- lavaan(RICLPMr_URS_DEV, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_URS_DEV.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_URS_DEV.fit)

#RSA
RICLPMr_URS_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA
  RIy =~ 1*t1WURSSg + 1*t2WURSSg + 1*t3WURSSg
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1WURSSg
  wy2 =~ 1*t2WURSSg
  wy3 =~ 1*t3WURSSg
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_URS_RSA.fit <- lavaan(RICLPMr_URS_RSA, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_URS_RSA.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_URS_RSA.fit)

##life satisfaction
#burnout
RICLPMr_LS_B <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1BURN + 1*t2BURN + 1*t3BURN
  RIy =~ 1*t1LS + 1*t2LS + 1*t3LS
  
  # Create within-person centered variables
  wx1 =~ 1*t1BURN
  wx2 =~ 1*t2BURN
  wx3 =~ 1*t3BURN
  wy1 =~ 1*t1LS
  wy2 =~ 1*t2LS
  wy3 =~ 1*t3LS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_LS_B.fit <- lavaan(RICLPMr_LS_B, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_LS_B.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_LS_B.fit)

#exhaustion
RICLPMr_LS_EXH <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1EXH + 1*t2EXH + 1*t3EXH
  RIy =~ 1*t1LS + 1*t2LS + 1*t3LS
  
  # Create within-person centered variables
  wx1 =~ 1*t1EXH
  wx2 =~ 1*t2EXH
  wx3 =~ 1*t3EXH
  wy1 =~ 1*t1LS
  wy2 =~ 1*t2LS
  wy3 =~ 1*t3LS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_LS_EXH.fit <- lavaan(RICLPMr_LS_EXH, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_LS_EXH.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_LS_EXH.fit)

#devaluation
RICLPMr_LS_DEV <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1DEV + 1*t2DEV + 1*t3DEV
  RIy =~ 1*t1LS + 1*t2LS + 1*t3LS
  
  # Create within-person centered variables
  wx1 =~ 1*t1DEV
  wx2 =~ 1*t2DEV
  wx3 =~ 1*t3DEV
  wy1 =~ 1*t1LS
  wy2 =~ 1*t2LS
  wy3 =~ 1*t3LS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_LS_DEV.fit <- lavaan(RICLPMr_LS_DEV, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_LS_DEV.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_LS_DEV.fit)

#RSA
RICLPMr_LS_RSA <- '
  # Create between components (random intercepts)
  RIx =~ 1*t1RSA + 1*t2RSA + 1*t3RSA
  RIy =~ 1*t1LS + 1*t2LS + 1*t3LS
  
  # Create within-person centered variables
  wx1 =~ 1*t1RSA
  wx2 =~ 1*t2RSA
  wx3 =~ 1*t3RSA
  wy1 =~ 1*t1LS
  wy2 =~ 1*t2LS
  wy3 =~ 1*t3LS
  
  # Estimate lagged effects between within-person centered variables 
  # (constrained)
  wx2 ~ a*wx1 + b*wy1 
  wy2 ~ c*wx1 + d*wy1
  wx3 ~ a*wx2 + b*wy2
  wy3 ~ c*wx2 + d*wy2
  
  # Estimate covariances between residuals of within-person centered variables 
  wx2 ~~ wy2
  wx3 ~~ wy3
  
  # Estimate covariance between within-person centered variables at first wave
  wx1 ~~ wy1 # Covariance
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy
  
  # Estimate (residual) variance of within-person centered variables 
  wx1 ~~ wx1 # Variance
  wy1 ~~ wy1 
  wx2 ~~ wx2 # Residual variance
  wy2 ~~ wy2 
  wx3 ~~ wx3 
  wy3 ~~ wy3 

'
RICLPMr_LS_RSA.fit <- lavaan(RICLPMr_LS_RSA, 
  data = dat2, 
  missing = 'ML',
  estimator = "MLR",
  meanstructure = T, 
  int.ov.free = T
) 
summary(RICLPMr_LS_RSA.fit, fit.measures=T, standardized = T)
standardizedsolution(RICLPMr_LS_RSA.fit)
```

# Model comparisons between standard and constrained models 
To see which of the models fits the data better.
```{r model comparisons}
##set degrees of freedom for all comparisons
df_riclpmr <- 4
df_riclpm <- 1

##depression
##burnout
# Step 1: Find indices needed for covariance matrix of random intercepts
vcov(RICLPM_DS_B.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_DS_B.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrdsb <- 3.01
Chi2_riclpmdsb <- 0.30

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestdsb <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrdsb, Chi2_riclpmdsb, df_riclpmr, df_riclpm)
ChiBar2DiffTestdsb$DiffChi2
ChiBar2DiffTestdsb$p_value

##exhaustion
# Step 1: Find indices needed for covariance matrix of random intercepts
vcov(RICLPM_DS_EXH.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_DS_EXH.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrdse <- 6.73
Chi2_riclpmdse <- 0.63

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestdse <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrdse, Chi2_riclpmdse, df_riclpmr, df_riclpm)
ChiBar2DiffTestdse$DiffChi2
ChiBar2DiffTestdse$p_value

##devaluation
vcov(RICLPM_DS_DEV.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_DS_DEV.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrdsd <- 5.49
Chi2_riclpmdsd <- 0.23

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestdsd <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrdsd, Chi2_riclpmdsd, df_riclpmr, df_riclpm)
ChiBar2DiffTestdsd$DiffChi2
ChiBar2DiffTestdsd$p_value

##rsa
vcov(RICLPM_DS_RSA.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_DS_RSA.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square and degrees of freedom
Chi2_riclpmrdsr <- 6.04
Chi2_riclpmdsr <- 1.62

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestdsr <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrdsr, Chi2_riclpmdsr, df_riclpmr, df_riclpm)
ChiBar2DiffTestdsr$DiffChi2
ChiBar2DiffTestdsr$p_value


##sleep quality
##burnout
# Step 1: Find indices needed for covariance matrix of random intercepts
vcov(RICLPM_SQ_B.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_SQ_B.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrsqb <- 2.71
Chi2_riclpmsqb <- 2.20

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestsqb <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrsqb, Chi2_riclpmsqb, df_riclpmr, df_riclpm)
ChiBar2DiffTestsqb$DiffChi2
ChiBar2DiffTestsqb$p_value

##exhaustion
# Step 1: Find indices needed for covariance matrix of random intercepts
vcov(RICLPM_SQ_EXH.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_SQ_EXH.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrsqe <- 8.41
Chi2_riclpmsqe <- 6.33

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestsqe <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrsqe, Chi2_riclpmsqe, df_riclpmr, df_riclpm)
ChiBar2DiffTestsqe$DiffChi2
ChiBar2DiffTestsqe$p_value

##devaluation
vcov(RICLPM_SQ_DEV.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_SQ_DEV.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrsqd <- 5.08
Chi2_riclpmsqd <- 2.4

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestsqd <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrsqd, Chi2_riclpmsqd, df_riclpmr, df_riclpm)
ChiBar2DiffTestsqd$DiffChi2
ChiBar2DiffTestsqd$p_value

##rsa
vcov(RICLPM_SQ_RSA.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_SQ_RSA.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square and degrees of freedom
Chi2_riclpmrsqr <- 3.325
Chi2_riclpmsqr <- 0.059

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestsqr <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrsqr, Chi2_riclpmsqr, df_riclpmr, df_riclpm)
ChiBar2DiffTestsqr$DiffChi2
ChiBar2DiffTestsqr$p_value


##physical symptoms
##burnout
# Step 1: Find indices needed for covariance matrix of random intercepts
vcov(RICLPM_PS_B.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_PS_B.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrpsb <- 6.67
Chi2_riclpmpsb <- 1.41

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestpsb <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrpsb, Chi2_riclpmpsb, df_riclpmr, df_riclpm)
ChiBar2DiffTestpsb$DiffChi2
ChiBar2DiffTestpsb$p_value

##exhaustion
# Step 1: Find indices needed for covariance matrix of random intercepts
vcov(RICLPM_PS_EXH.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_PS_EXH.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrpse <- 5.88
Chi2_riclpmpse <- 0.038

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestpse <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrpse, Chi2_riclpmpse, df_riclpmr, df_riclpm)
ChiBar2DiffTestpse$DiffChi2
ChiBar2DiffTestpse$p_value

##devaluation
vcov(RICLPM_PS_DEV.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_PS_DEV.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrpsd <- 3.17
Chi2_riclpmpsd <- 0.1

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestpsd <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrpsd, Chi2_riclpmpsd, df_riclpmr, df_riclpm)
ChiBar2DiffTestpsd$DiffChi2
ChiBar2DiffTestpsd$p_value

##RSA
vcov(RICLPM_PS_RSA.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_PS_RSA.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrpsr <- 10.35
Chi2_riclpmpsr <- 6.87

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestpsd <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrpsr, Chi2_riclpmpsr, df_riclpmr, df_riclpm)
ChiBar2DiffTestpsd$DiffChi2
ChiBar2DiffTestpsd$p_value


##WURSS
##burnout
# Step 1: Find indices needed for covariance matrix of random intercepts
vcov(RICLPM_URS_B.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_URS_B.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrursb <- 3.45
Chi2_riclpmursb <- 0.00

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestursb <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrursb, Chi2_riclpmursb, df_riclpmr, df_riclpm)
ChiBar2DiffTestursb$DiffChi2
ChiBar2DiffTestursb$p_value

##rsa
vcov(RICLPM_URS_RSA.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_URS_RSA.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square and degrees of freedom
Chi2_riclpmrursr <- 7.44
Chi2_riclpmursr <- 0.006

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestursr <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrursr, Chi2_riclpmursr, df_riclpmr, df_riclpm)
ChiBar2DiffTestursr$DiffChi2
ChiBar2DiffTestursr$p_value

##life satisfaction
##burnout
# Step 1: Find indices needed for covariance matrix of random intercepts
vcov(RICLPM_LS_B.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_LS_B.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrlsb <- 8.45
Chi2_riclpmlsb <- 0.033

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestlsb <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrlsb, Chi2_riclpmlsb, df_riclpmr, df_riclpm)
ChiBar2DiffTestlsb$DiffChi2
ChiBar2DiffTestlsb$p_value

##exhaustion
# Step 1: Find indices needed for covariance matrix of random intercepts
vcov(RICLPM_LS_EXH.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_LS_EXH.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrlse <- 7.14
Chi2_riclpmlse <- 0.4

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestlse <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrlse, Chi2_riclpmlse, df_riclpmr, df_riclpm)
ChiBar2DiffTestlse$DiffChi2
ChiBar2DiffTestlse$p_value

##devaluation
vcov(RICLPM_LS_DEV.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_LS_DEV.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square
Chi2_riclpmrlsd <- 6.24
Chi2_riclpmlsd <- 0.22

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestlsd <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrlsd, Chi2_riclpmlsd, df_riclpmr, df_riclpm)
ChiBar2DiffTestlsd$DiffChi2
ChiBar2DiffTestlsd$p_value

##rsa
vcov(RICLPM_LS_RSA.fit) # Full covariance matrix
indices <- c(22, 23) # The 22nd and 23rd indices regard random intercepts
q <- length(indices) # Number of random intercepts
S <- vcov(RICLPM_LS_RSA.fit)[indices, indices] # Extract covariance matrix of random intercepts

# Step 2: Input Chi-square and degrees of freedom
Chi2_riclpmrlsr <- 8.06
Chi2_riclpmlsr <- 0.42

# Step 3: Perform Chi-bar-square test (and obtain Chi-bar-square weights)
ChiBar2DiffTestlsr <- ChiBarSq.DiffTest(q, S, Chi2_riclpmrlsr, Chi2_riclpmlsr, df_riclpmr, df_riclpm)
ChiBar2DiffTestlsr$DiffChi2
ChiBar2DiffTestlsr$p_value
```

